Soss: Declarative Probabilistic Programming via Runtime Code Generation

### 2021-09-21 paper/paper.tex
final version

%%%% Small single column format
\documentclass[anonymous=false, %
               format=acmsmall, %
               review=true, %
               screen=true, %
               nonacm=true]{acmart}

@@

\author{Chad Scherrer}
\orcid{0000-0002-1490-0304}
\affiliation{%
  \institution{RelationalAI}
  % \department{Department of Brain and Cognitive Sciences}
  %\streetaddress{43 Vassar St}
  \city{Seattle}
  \state{WA}
  %\postcode{02139}
  %\country{USA}
}
\email{chad.scherrer@gmail.com}

\author{Taine Zhao}
%\orcid{1234-5678-9012-3456}
\affiliation{%
  \institution{University of Tsukuba}
  \department{Department of Computer Science}
  %\streetaddress{625 Mt Auburn St #3}
  %\city{Cambridge} 
  %\state{MA}
  %\postcode{02138}
  %\country{USA}
}
\email{thaut@logic.cs.tsukuba.ac.jp}
%\renewcommand\shortauthors{Mage, M. et al}

@@

\begin{description}  
    \item[\texttt{rand}] draws a random point or sample from a given distribution.
    \item[\texttt{particles}] draws a \emph{systematic sample} using \jl#MonteCarloMeasurements.jl# \cite{8ff6a743-0ad6-4d98-bbb3-5d549c698bc1}.
    \item[\texttt{logpdf}] takes a distribution and a point, and returns the log-density at that point.
    \item[\texttt{xform}] takes a distribution and some known data, and returns a bijection from $\mathbb{R}^n$ to the space of unknowns. This is useful for algorithms like Hamiltonian Monte Carlo \cite{Neal2011}.
    \item[\texttt{symlogpdf}] takes a model, and returns a SymPy \cite{10.7717/peerj-cs.103} representation of the log-density, with some additional Julia-based simplifications.
    \item[\texttt{codegen}] calls \jl#symlogpdf#, and uses the result to generate a more efficient version of \jl#logpdf#.
\end{description}

>>>>

%%%% Small single column format
\documentclass[anonymous=false, %
               format=acmsmall, %
               review=false, %
               screen=true, %
               nonacm=true]{acmart}

@@

\author{Chad Scherrer}
\orcid{0000-0002-1490-0304}
\affiliation{%
  \institution{RelationalAI}
  % \department{Department of Brain and Cognitive Sciences}
  %\streetaddress{43 Vassar St}
  \city{Seattle}
  \state{WA}
  %\postcode{02139}
  \country{USA}
}
\email{chad.scherrer@gmail.com}

\author{Taine Zhao}
%\orcid{1234-5678-9012-3456}
\affiliation{%
  \institution{University of Tsukuba}
  \department{Department of Computer Science}
  %\streetaddress{625 Mt Auburn St #3}
  %\city{Cambridge} 
  %\state{MA}
  %\postcode{02138}
  \country{Japan}
}
\email{thaut@logic.cs.tsukuba.ac.jp}
%\renewcommand\shortauthors{Mage, M. et al}

@@

\begin{description}
    \item[\texttt{rand}] draws a random point or sample from a given distribution.
    \item[\texttt{particles}] draws a \emph{systematic sample} using \jl#MonteCarloMeasurements.jl# \cite{bagge2020MCM.jl}.
    \item[\texttt{logpdf}] takes a distribution and a point, and returns the log-density at that point.
    \item[\texttt{xform}] takes a distribution and some known data, and returns a bijection from $\mathbb{R}^n$ to the space of unknowns. This is useful for algorithms like Hamiltonian Monte Carlo \cite{Neal2011}.
    \item[\texttt{symlogpdf}] takes a model, and returns a SymPy \cite{10.7717/peerj-cs.103} representation of the log-density, with some additional Julia-based simplifications.
    \item[\texttt{codegen}] calls \jl#symlogpdf#, and uses the result to generate a more efficient version of \jl#logpdf#.
\end{description}
